\documentclass[a4paper,11pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{comment} % enable \begin{comment} ... \end{comment} blocks

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\urlstyle{same}

\newcommand{\sectionheading}[1]{\subsection*{\textcolor{purple}{#1}}}

\begin{document}

\begin{center}
    \LARGE{\href{https://scholar.google.com/citations?hl=en&user=f-ZPkk0AAAAJ}{\textbf{Prem Kumar}}} \\[0.2cm]
    \large{Ph.D. Student} \\[0.1cm]
    \large{The Institute of Mathematical Sciences (IMSc), Chennai, India} \\[0.1cm]
    Website: \href{https://prem314.github.io}{prem314.github.io}\\
    Email: \href{mailto:premkr@imsc.res.in}{premkr@imsc.res.in}, \href{mailto:prem3141592@gmail.com}{prem3141592@gmail.com} \\[0.1cm]
\end{center}


\sectionheading{Education and Training}
\begin{itemize}[leftmargin=*,label={}]
    \item \textbf{Ph.D. in Theoretical Physics} \hfill 2021-Present \\
          Institute of Mathematical Sciences (IMSc), Chennai, India \\
          PhD supervisor: \href{https://scholar.google.com/citations?user=zr0J0lMAAAAJ&hl=en&oi=ao}{Prof. Sibasish Ghosh}
    \item \textbf{M.Sc. in Physics} \hfill 2019-2021 \\
          Institute of Mathematical Sciences (IMSc), Chennai, India \\
%          Project: Dynamics of open quantum Systems: Different approaches to non-Markovianity \\
          MSc project supervisor: \href{https://scholar.google.com/citations?user=zr0J0lMAAAAJ&hl=en&oi=ao}{Prof. Sibasish Ghosh}
    \item \textbf{B.Sc. in Physics, Maths, Electronics} \hfill 2016 - 2019\\
    Christ (Deemed to be University), Bangalore, India
\end{itemize}

\sectionheading{Research Highlights}
\begin{itemize}[leftmargin=*]
	\item Analytical derivation of the 4th-order Time-Convolutionless (TCL4) generator for Spin-Boson models, benchmarking it against exact numerical methods. We also studied the corrections to the steady state and non-Markovianity of the dynamics.
	\item Generalized the ultra-strong coupling limit quantum mean force Gibbs state to a large class of anharmonic environments.
\end{itemize}


\sectionheading{Publications}

\textbf{\textit{Refereed Journal Publications}}
\begin{enumerate}[leftmargin=*,label=\arabic*.]
    \item Prem Kumar, K. P. Athulya, and Sibasish Ghosh. \textbf{``Asymptotic TCL4 Generator for the Spin-Boson Model: Analytical Derivation and Benchmarking."} \textit{\href{https://doi.org/10.1103/69y3-x6vh}{Physical Review B}} (2025).
    \item Prem Kumar, K. P. Athulya, and Sibasish Ghosh. \textbf{``Equivalence between the second order steady state for the spin-boson model and its quantum mean force Gibbs state."} \textit{\href{https://doi.org/10.1103/PhysRevB.111.115423}{Physical Review B}} 111, 115423 (2025).
    \item Prem Kumar, and Sibasish Ghosh. \textbf{``Ultrastrong coupling limit to quantum mean force Gibbs state for anharmonic environment."} \textit{\href{https://doi.org/10.1063/5.0223734}{The Journal of Chemical Physics}} 161, 17 (2024).
\end{enumerate}

\textbf{\textit{Pedagogical Reviews}}
\begin{itemize}[leftmargin=*]
    \item Prem Kumar. \textbf{``Local harmonic approximation to quantum mean force Gibbs state"} \href{https://arxiv.org/abs/2401.11595}{arXiv:2401.11595} (2024).
    \\[0.1cm]
    \footnotesize{\textit{Note: A unified derivation and review of the harmonic approximation method for mean force Gibbs state.}}
\end{itemize}


\sectionheading{Technical Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Computational Physics \& ML:} 
    \begin{itemize}
        \item \textbf{Tensor Networks:} Implementation of algorithms for simulating open quantum system dynamics.
        \item \textbf{Machine Learning:} \textbf{PyTorch} for machine learning and designing transformer models.
        \item \textbf{Languages:} Python (QuTiP, NumPy, SciPy).
    \end{itemize}
    \item \textbf{Symbolic Computing (Mathematica):} 
    \begin{itemize}
        \item Developed \href{https://github.com/prem314/spin-boson-tcl4}{\texttt{spin-boson-tcl4}}: An open-source package for the symbolic derivation and implementation of 4th-order Time-Convolutionless (TCL) master equations.
    \end{itemize}
\end{itemize}





\sectionheading{List of presentations and participations at conferences}
\begin{enumerate}
  \item Poster presentation on \textit{``Asymptotic TCL4 Generator for the Spin-Boson Model: Analytical Derivation and Benchmarking''}, Quantum Foundations Technology and Applications (QFTA-2025), IISER Mohali, India, 4--8 December 2025.
  \item Poster presentation on \textit{``Ultrastrong coupling limit to quantum mean force Gibbs state for anharmonic environment''}, \href{https://quantum25.dpg-tagungen.de/}{Second DPG Fall Meeting: 100 Years of Quantum Physics}, Georg-August-Universität Göttingen, Germany, 8--12 September 2025.
  \item Poster presentation on \textit{``Equivalence between the second order steady state for the spin-boson model and its quantum mean force Gibbs state''}, \href{https://www.iiserkol.ac.in/~qm100/}{``100 Years of Quantum Mechanics''}, IISER Kolkata, India, 18--21 December 2024.
  \item Poster presentation on \textit{``Ultrastrong coupling limit to quantum mean force Gibbs state for anharmonic environment''}, \href{https://quantum.iitm.ac.in/qcmc24/}{QCMC-24: International Conference on Quantum Communication, Measurement and Computing}, IIT Madras, Chennai, India, 26--30 August 2024.
\end{enumerate}

\sectionheading{Research visits and seminars}
\begin{enumerate}
    \item {\it ``Quantum mean force Gibbs state in weak and ultra-strong coupling limits''}, Academic visit, ``Department of Mathematical Physics, Nicolaus Copernicus University, Torun, Poland'', Sept 15-19,
    \item Seminar on {\it ``Equilibrium state and dynamics of an open quantum system in weak and strong coupling limits''}, Academic visit, IIT-H, May 7-9 2025.
\end{enumerate}


\sectionheading{Achievements}
\begin{itemize}[leftmargin=*]
    \item JEST 2019: All India Rank 75, Percentile: 98.89
    \item JAM 2019: All India Rank 146, Percentile: 99.06
    \item During BSc, won 1st prize in State level Inter-Collegiate Fest, Jyoti Nivas College, Bangalore, February 2018 for building  \href{https://www.youtube.com/watch?v=04tWPuDVBhs}{a 20-bit programmable computer on breadboard.}
\end{itemize}


\sectionheading{Professional References}



\textbf{Dr. Sibasish Ghosh} \\
Professor \\
Optics and Quantum Information Group \\
The Institute of Mathematical Sciences \\
Chennai - 600113, India \\
e-mail: \textsl{sibasish@imsc.res.in}

\vspace{0.5cm}



\end{document}
